### 2011-05-06 paper/paper.tex

To test how these algorithms performed in practice, we implemented five algorithms for sampling: ball-walking, adaptive ball-walking, Gaussian-walking, adaptive Gaussian-walking, and hit-and-run. The five methods were implemented in C++ and tested on several test regions of various dimensions: a cube, a sphere, and a regular simplex, all definied by separation oracles. Real numbers were represented by 64-bit double precision, although random numbers were generated with 31 bits. We chose not to implement higher precision floating point numbers because our interest is in the scaling with dimension, rather than with the sample's requested precision.

>>>>

To test how these algorithms performed in practice, we implemented five algorithms for sampling: ball-walking, adaptive ball-walking, Gaussian-walking, adaptive Gaussian-walking, and hit-and-run. The five methods were implemented in C++ and tested on several test regions of various dimensions: a cube, a sphere, and a regular simplex, all defined by separation oracles. Real numbers were represented by 64-bit double precision, although each random number was generated from 31 random bits. We chose not to implement higher precision floating point numbers because our interest is in the scaling with dimension, rather than with the sample's requested precision.
